P. berghei pir - Sample clustering/PCA

### 2021-12-03 chapter3_results_bergheiPir/Pberghei_pir_samples_hclust-PCA-topGenes.Rmd
Create expt_tpms object and change function to use it

```{r read_tpm}
berghei_tpm <- read.csv('berghei_tpm.csv', 
                        row.names = 1)
```

@@

```{r bandwidth}
# Compute the average bandwidth for all the samples so that we have the same value for each figure.
list_bw = lapply(expt_tpms, function(expt){ 
  lapply(colnames(expt$tpm)[-1], 
         function(sample){
           data = as.numeric(unlist(select(expt$tpm, 
                                           paste(sample))))
           dens = density(log1p(data))
           dens$bw
         })
})
bw_mean = mean(unlist(list_bw))
bw_range = max(unlist(unlist(list_bw))) - min(unlist(unlist(list_bw)))
print(paste('Bandwidth range = ', bw_range))
```

>>>>

```{r read_tpm}
berghei_tpm <- read.csv('berghei_tpm.csv', 
                        row.names = 1)
expt_tpms <- lapply(paste0('E0', seq(1,10)),
                    function(Enum){
                      df <- berghei_tpm[,str_subset(colnames(berghei_tpm), 
                                              pattern = paste0('Geneid|',Enum))]
                    })
names(expt_tpms) <- paste0('E0', seq(1,10))
```

@@

```{r bandwidth}
# Compute the average bandwidth for all the samples so that we have the same value for each figure.
list_bw = lapply(expt_tpms, function(expt){ 
  lapply(colnames(expt)[-1], 
         function(sample){
           data = as.numeric(unlist(select(expt, 
                                           paste(sample))))
           dens = density(log1p(data))
           dens$bw
         })
})
bw_mean = mean(unlist(list_bw))
bw_range = max(unlist(unlist(list_bw))) - min(unlist(unlist(list_bw)))
print(paste('Bandwidth range = ', bw_range))
```
